FraCaS: Temporal Analysis

### 2020-06-22 paper2020/paper.tex
minor

\paragraph{Montagovian semantics}

@@

\paragraph{Dynamic semantics}
We additionally assume support for (non-temporal) anaphora, using a
monadic-based dynamic semantics
\cite{unger_dynamic_2011,charlow_monadic_2015,charlow_modular_2017}.
Our particular implementation is not perfect \ifanon (citations
anonymized) \else \citet{bernardy_wide-coverage_2019} \fi but non-temporal
anaphoroi in the testsuite are generally resolved as they should be.

@@

\section{Our Treatment of time}
\label{sec:our-semantics}

@@

\paragraph{temporal context}

@@

\paragraph{tenses}

@@

\paragraph{temporal adverbs}

@@

\paragraph{(un)repeatable achievements}
\label{sec:repeatable-achievements}
The principle of using unicity of action interacts well with the usual
interpretation of quantifiers (and anaphora).  Indeed, using it, we
can refute problem (279), as expected by the testsuite:

@@

\paragraph{action-modification verbs}

@@

\paragraph{Progressive aspect}

@@

\section{Results and evaluation}
\label{sec:results}
Our target is the FraCaS testsuite, which aims at covering a wide
range of common natural-language phenomena. The testsuite is structured in 9 sections:

@@

The issue is that the quantification introduced by the temporal marker
is outside the negation. For example, the premiss of (038) is
interpreted as ``there exists a time in the past when every delegate
did not finish the report'' --- which is incorrect in this context.
\fracasex{038}{
\item	No delegate finished the report.
\hyp 	Some delegate finished the report on time.
}
%
We stress that such interaction between quantifiers and negation
already occurs without temporal analysis: one must make a difference
between narrow scoping and wide scoping \cite{todo}\todo{Stergios?}. Unfortunately,
the montagovian system over which we base our implementation does not
support this phenomena. (In fact the FraCaS test suite does not appear to
test if the difference between narrow and wide scoping is handled properly.)
We propose that the situation becomes
quantitatively more difficult to handle with the added complication of
time-quantification, but not fundamentally different.
%
A similar issue occurs with group readings, which are interpreted as
conjunctions. Here, the problem is to solve the order of scoping
between this conjunction and time-interval quantifiers.

>>>>

\paragraph{Montagovian Semantics}

@@

\paragraph{Dynamic Semantics}
We additionally assume support for (non-temporal) anaphora, using a
monadic-based dynamic semantics
\cite{unger_dynamic_2011,charlow_monadic_2015,charlow_modular_2017}.
Our particular implementation is not perfect \ifanon (citations
anonymized) \else \citet{bernardy_wide-coverage_2019} \fi but non-temporal
anaphoroi in the testsuite are generally resolved as they should be.

@@

\section{Our Treatment of Time}
\label{sec:our-semantics}

@@

\paragraph{Temporal Context}

@@

\paragraph{Tenses}

@@

\paragraph{Temporal Adverbs}

@@

\paragraph{(Un)repeatable Achievements}
\label{sec:repeatable-achievements}
The principle of using unicity of action interacts well with the usual
interpretation of quantifiers (and anaphora).  Indeed, using it, we
can refute problem (279), as expected by the testsuite:

@@

\paragraph{Action-modification Verbs}

@@

\paragraph{Progressive Aspect}

@@

\section{Results and Evaluation}
\label{sec:results}
Our target is the FraCaS testsuite, which aims at covering a wide
range of common natural-language phenomena. The testsuite is structured in 9 sections:

@@

The issue is that the quantification introduced by the temporal marker
is outside the negation. For example, the premiss of (038) is
interpreted as ``there exists a time in the past when every delegate
did not finish the report'' --- which is incorrect in this context.
\fracasex{038}{
\item	No delegate finished the report.
\hyp 	Some delegate finished the report on time.
}
%
We stress that such interaction between quantifiers and negation
already occurs without any temporal analysis: one must make a difference
between narrow  and wide scope.\footnote{The literature on wide and narrow scope readings of quantifiers and quantifiers and negation is vast. We direct the reader to \cite{steedman:2012} for a comprehensive and thorough discussion of the relevant issues.} Unfortunately,
the Montagovian system over which we base our implementation does not
support these phenomena. (In fact the FraCaS test suite does not appear to
test if the difference between narrow and wide scoping is handled properly.)
We propose that the situation becomes
quantitatively more difficult to handle with the added complication of
time-quantification, but not fundamentally different.
%
A similar issue occurs with group readings, which are interpreted as
conjunctions. Here, the problem is to solve the order of scoping
between this conjunction and time-interval quantifiers.
